\Large Bayer network classifiers for fRMI

### 2012-09-14 proposal/proposal.tex
minor changes
Added section on programmign language, extended gitignore

\title{\Large Out title here}
\author{\small Mattijs Meiboom (student number), Robin Mills (student number)\\
			\small Tijn Schouten (student number), Spyros Ioakeimidis (2144603)}
\date{\small \today}

@@

The chosen programming language is Python. We have chosen Python because ...

>>>>

\title{\Large Bayer network classifiers for fRMI}
\author{\small Mattijs Meiboom (s1398342), Robin Mills (s1544179)\\
			\small Tijn Schouten (s1836560), Spyros Ioakeimidis (s2144603)}
\date{\small \today}

@@

We have chosen to implement our classification algorithms using Python. To be specific,  the well-known SciPy library. SciPy is open-source software for mathematics, science, and engineering and offers similar functionality compared to MatLab. Even though our datasets have been stored in MatLab's \textit{.mat} format, SciPy can work with this as well.

The main motivation for chosing Python over MatLab is our familiarity with Python, its performance and its clean coding style. As an added benefit, anyone is able to reproduce our classification results even if they don't own a MatLab license.

Note that in the end, the specific choice is trivial with respect to our results. Both MatLab and Python (with some added libraries) support similar functionality.
